The ChEMBL database as Linked Open Data

### 2012-08-10 article.tex
Added twitter accounts

\author{Egon~L.~Willighagen$^{1,*}$\email{Egon~L.~Willighagen - egon.willighagen@maastrichtuniversity.nl}\and
Andra~Waagmeester$^1$\email{Andra Waagmeester - andra.waagmeester@maastrichtuniversity.nl}\and
Ola Spjuth$^2$\email{Ola Spjuth - ola.spjuth@farmbio.uu.se}\and
Peter~Ansell$^3$\email{Peter Ansell - p\_ansell@yahoo.com}\and
Antony~J.~Williams$^4$\email{Antony J. Williams - WilliamsA@rsc.org}\and
Valery~Tkachenko$^4$\email{Valery Tkachenko - TkachenkoV@rsc.org}\and
Janna~Hastings$^5$\email{Janna Hastings - hastings@ebi.ac.uk}\and
Mark~Davies$^6$\email{Mark Davies - mdavies@ebi.ac.uk}\and
John~P.~Overington$^6$\email{John P. Overington - jpo@ebi.ac.uk}\and
Anna~Gaulton$^6$\email{Anna Gaulton - agaulton@ebi.ac.uk}\and
Bin~Chen$^7$\email{Bin Chen - binchen@indiana.edu}\and
David~J.~Wild$^7$\email{David J. Wild - djwild@indiana.edu}
}

>>>>

\author{Egon~L.~Willighagen$^{1,*}$\email{Egon~L.~Willighagen - egon.willighagen@maastrichtuniversity.nl, \url{http://twitter.com/egonwillighagen}}\and
Andra~Waagmeester$^1$\email{Andra Waagmeester - andra.waagmeester@maastrichtuniversity.nl}\and
Ola Spjuth$^2$\email{Ola Spjuth - ola.spjuth@farmbio.uu.se}\and
Peter~Ansell$^3$\email{Peter Ansell - p\_ansell@yahoo.com}\and
Antony~J.~Williams$^4$\email{Antony J. Williams - WilliamsA@rsc.org, \url{http://twitter.com/ChemConnector}}\and
Valery~Tkachenko$^4$\email{Valery Tkachenko - TkachenkoV@rsc.org}\and
Janna~Hastings$^5$\email{Janna Hastings - hastings@ebi.ac.uk}\and
Mark~Davies$^6$\email{Mark Davies - mdavies@ebi.ac.uk\url{http://twitter.com/mdavies12}}\and
John~P.~Overington$^6$\email{John P. Overington - jpo@ebi.ac.uk}\and
Anna~Gaulton$^6$\email{Anna Gaulton - agaulton@ebi.ac.uk}\and
Bin~Chen$^7$\email{Bin Chen - binchen@indiana.edu, \url{http://twitter.com/binchenindiana}}\and
David~J.~Wild$^7$\email{David J. Wild - djwild@indiana.edu, \url{http://twitter.com/davidjohnwild}}
}
